Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-16 paper/sheaf_lics.tex
formalization update lines

A Coq formalization is available at
\url{https://github.com/KevinQuirin/sheafification/}.
%
It is based on the homotopy type theory library available at
\url{https://github.com/HoTT/HoTT}

Formalisation of subobject classifiers has been done in
\texttt{sub\_object\_classifier.v}, 284 lines.

Colimits, $p$-pullbacks and \v{C}ech nerves has been formalized in
\texttt{colimits.v, cech\_nerve.v}, 552 lines.

Reflective subuniverses and modalities are formalized in
\texttt{reflective\_subuniverse.v, modalities.v}, 1053 lines.

Definition of th reflective subuniverse on $\HProp$ is given in
\texttt{sheaf\_base\_case.v}, 186 lines.

Section~\ref{sec:sheaves} is formalized in
\texttt{sheaf\_def\_and\_thm.v}, 1029 lines.

Section~\ref{sec:sheafification} is formalized in
\texttt{sheaf\_induction.v}, 2340 lines.

At total, with other files containing technical lemmas, the project
contains 6322 lines.
%\nt{describe how many line for each, be clear about what has not been formalized}

>>>>

A Coq formalization is available at
\url{https://github.com/KevinQuirin/sheafification/}.
%
It is based on the homotopy type theory library available at
\url{https://github.com/HoTT/HoTT}
\begin{itemize}
\item Formalisation of subobject classifiers has been done in
\texttt{sub\_object\_classifier.v}, 284 lines.
\item 
Colimits, $p$-pullbacks and \v{C}ech nerves has been formalized in
\texttt{colimits.v, cech\_nerve.v}, 552 lines.
\item 
Reflective subuniverses and modalities are formalized in
\texttt{reflective\_subuniverse.v, modalities.v}, 1053 lines.
\item 
Definition of th reflective subuniverse on $\HProp$ is given in
\texttt{sheaf\_base\_case.v}, 186 lines.
\item 
Section~\ref{sec:sheaves} is formalized in
\texttt{sheaf\_def\_and\_thm.v}, 1029 lines.
\item 
Section~\ref{sec:sheafification} is formalized in
\texttt{sheaf\_induction.v}, 2340 lines.
\end{itemize}
At total, with other files containing technical lemmas, the project
contains 6322 lines.
%\nt{describe how many line for each, be clear about what has not been formalized}
